\section{Reflection}
In this section I will give a reflection of my process in creating this thesis and the final results. I started working on this thesis in the summer of 2021. For the first few months the goal of the thesis wasn't entirely clear. I knew I wanted to research map merging but didn't know in which context I would do so. I also felt that I had trouble aligning my view of what I wanted to research with those of my supervisors. This might have been made worse by the fact that I had three supervisors with significantly different perspectives. My own frustration with my slow progress demotivated me, alhtough not to the point of not getting any work done. This problem continued until shortly before my P2. Although at that point my methodology was not nearly defined yet I knew what I wanted to research. Unfortunately, this did not leave me with enough time to polish my P1 report to my own satisfaction. I was especially dissatisfied with the maths part of the report because I had very little experience with this. Nevertheless, my P1 was well received by my supervisors, although they did express their concerns with the amount of work that needed to be done. I noted that the amount of work was large, but not impossible for me to complete. 

Between my P2 and P3 I mostly worked on map extraction component. The good results achieved here motivated me to make a large amount of progress during this time. However, at this point my approach to map matching and map fusion were still unclear to me. In hindsight, I should have defined my entire methodology before implementing any parts. The problem with that is that I enjoy programming much more than writing or researching, and I was unable to resist the temptation to work on what I enjoy instead of what needed to be done. I completed my work on the map extraction component before my P3, which was well received.

After my P3 I needed to start working on the map matching and map fusion components. In contract to my work on map extraction, progress on map matching was very slow. Although my initial idea for my methodology wasn't far off from my final one, I had a lot of trouble getting a working implementation. Approaches that in my mind should work, in fact did not. As my P4 date approached I still had not finished the map matching component, let alone the map fusion component. Coincidentally, about a month before my P4 date I was told that I did not have the required ECTS to participate, and that I would have to wait until next semester to do my P4. This gave me some relief, as I now had the time to properly finish what I started. Between my initial P4 date and my actual one I mostly worked on getting map matching and map fusion working, which I did eventually. Unfortunately, this did not leave me with much time to finish this report. I worked hard to get everything written down, which I feel like I succeeded at, but there were still a lot of things that I would have liked to add. My P4 was again well received, with most comments being about mathematical notation, which I have fixed for my P5 document. 
Overall, I am satisfied with my results but not with my process. I took on too much work to finish in the allotted time and often left parts that I did not enjoy to the last moment. Nevertheless, I feel I have learned from the experience the things that I wanted to, which for me was the ultimate goal of this project. I am also happy with the contribution of my supervisors, who had to spend a lot of time listening to me talk about my various ideas. Although their multitude of perspectives at some points led to frustration on my part, I feel that in the end it contributed positively to my process and results.